A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-09-10 paper/paper.tex
paper: define semi-{simplicial, cubical} sets combinatorially

% Simplicial and Cubical sets
\newcommand{\DeltaHat}{\ensuremath{\hat{\boldsymbol{\Delta}}}}
\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
\renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}

@@

\subsection{Semi-simplicial sets}
Semi-simplicial sets are otherwise known as \emph{delta-sets} in mathematical literature. We briefly describe \DeltaHat, which is identical to \Simplex{}, but for the fact that the maps $\sq{m} \rightarrow \sq{n}$ are \emph{strictly} order-preserving. The degeneracies then vanish, and we're left with the task of defining gluing conditions solely on the basis of face maps. The core of the definition of $\SSet$ is precisely what we have constructed.

\begin{example}[$\DeltaHat^0$, $\DeltaHat^1$, $\DeltaHat^2$]
  $\DeltaHat^0$ can be drawn as:
  \begin{equation*}
    \begin{tikzcd}
      \bullet
    \end{tikzcd}
  \end{equation*}

  $\DeltaHat^1$ can be drawn as:
  \begin{equation*}
    \begin{tikzcd}
      \bullet \arrow[r, dash] & \bullet
    \end{tikzcd}
  \end{equation*}

  $\DeltaHat^2$ can be drawn as:
  \begin{equation*}
    \begin{tikzcd}
      & \bullet\arrow[dr, dash] & \\
      \bullet\arrow[rr, dash]\arrow[ur, dash] && \bullet
    \end{tikzcd}
  \end{equation*}
\end{example}

\subsection{Semi-cubical sets}
\begin{definition}[\Cube{n}]
  \begin{equation*}
    \Cube{n} := \I{n} = \sq{0, 1}^n
  \end{equation*}
\end{definition}

@@

  $$
    \begin{tikzcd}
      0 \equiv 1
    \end{tikzcd}
  $$

@@

  and $\Cube{2}$ can be drawn as:

>>>>

% Simplicial and Cubical sets
\newcommand{\DeltaPlus}{\ensuremath{\boldsymbol{\Delta}_+}}
\newcommand{\Cube}[1]{\ensuremath{\boldsymbol{\square^{#1}}}}
\renewcommand{\I}[1]{\ensuremath{\mathsf{I}^{#1}}}
\newcommand{\CSet}{\ensuremath{\mathsf{Set}_{\boldsymbol{\square}}}}

@@

\subsection{Augmented semi-simplicial sets}
We consider the category of augmented semi-simplices, which can be written in different ways, up to equivalence. We proceed to describe to combinatorial definition.
\begin{definition}[\DeltaPlus]
  The category of augmented semi-simplices is defined in terms of objects and morphisms:

  \begin{align*}
    \obj(\DeltaPlus) & := \Nat                                                                            \\
    \hom(p, n)       & := \{i_{p + 1}, \ldots, i_n \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\} \\
    f \circ g        & := \text{concatenation of the sequences $f$ and $g$}
  \end{align*}
\end{definition}

\begin{example}[$\DeltaPlus^0$, $\DeltaPlus^1$]
  $\DeltaPlus^0$ can be drawn as:

  $\DeltaPlus^1$ can be drawn as a filled triangle:

  \begin{equation*}
    \begin{tikzcd}
      & 2 \arrow[dr, dash] & \\
      0 \arrow[rr, dash]\arrow[ur, dash] && 1
    \end{tikzcd}
  \end{equation*}
\end{example}

\subsection{Semi-cubical sets}
\begin{definition}[\Cube{}]
  \begin{align*}
    \obj(\Cube{}) & := \Nat                                                                                                             \\
    \hom(p, n)    & := \{(i_{p + 1}, \epsilon_{p + 1}) \ldots, (i_n, \epsilon_n) \mid p < i_{p + 1} < i_{p + 2} < \ldots < i_n \leq n\}
  \end{align*}
\end{definition}

@@

  \begin{equation*}
    \begin{tikzcd}
      0 \equiv 1
    \end{tikzcd}
  \end{equation*}

@@

  and $\Cube{2}$ can be drawn as a filled square:
